---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

if (!require(tidyverse)) {install.packages("tidyverse")}
if (!require(lubridate)) {install.packages("lubridate")}
if (!require(glue)) {install.packages("glue")}
```
# CV

RMarkdown code for building CV and resumes from education, experience, accomplishment, project and
skills stored as CSV files and publications stored as BibTeX file. Code depends
on vitae package. Template is combination of vitae::hyndman and
template by Steven Miller (http://svmiller.com/blog/2016/03/svm-r-markdown-cv/).

## Example
```{r}
if (!require(tidyverse)) {install.packages("tidyverse")}
if (!require(vitae)) {install.packages("vitae")}
folder_path = "input/data"
# Experience section
df_experience <- read_csv(file.path(folder_path, "experience.csv"))

df_experience %>% 
  detailed_entries(
  with = title,
  what = unit,
  why = detail,
  when = glue::glue("{startMonth} {startYear} --> {endMonth} {endYear}",.na = ""),
  where = where
  )
```

# Projects

RMarkdown code for building projects with reveal.js which can be used to create yet another style of HTML5 slides based on the JavaScript library reveal.js. 
